### 2020-03-16 random/career_preparation/cover_letters/JD.tex
simple website in js/

\begin{letter}{Skydio \\ 114 Hazel Ave \\ Redwood City, CA 94061}

\opening{\textbf{Dear Skydio,}}

I am interested in being an Autonomy Intern for Summer 2020.

I believe I have the qualifications in machine learning, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of drone technology. Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. I am looking to further my understanding of the stack by working on embedded machine learning.

I have taken an electronics course, where we built radios, stopwatches, and other things in VDHL, as well as an interactive devices course that taught 3D printing and wearable device building. My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice. The current solution is tractors and manually dispersing the salt. I would like to see drones be able to quickly provide a map of unwalkable locations and report this to people cleaning up snow.

>>>>

\begin{letter}{JD \\ JD Building, No. 18 \\ Kechuang 11 Street \\ BDA, Beijing, 101111}

\opening{\textbf{Dear JD,}}

I am interested in being a Research Intern for Summer 2020.

I believe I have the qualifications in programming, machine learning, and cloud service management to develop and deploy valuable and performant models.
Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
I am looking to work on larger and more complex models that operate with a great deal of data.

I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
I have built reinforcement learning environements using OpenAI's Gym package and am excited to implement larger models in production.
My ideal conversation with an employee would be about how AI is changing the industry and what creative uses of AI in commerce there are.

### 2020-03-16 random/career_preparation/cover_letters/impossible.tex
simple website in js/

\begin{letter}{JD \\ JD Building, No. 18 \\ Kechuang 11 Street \\ BDA, Beijing, 101111}

\opening{\textbf{Dear JD,}}

I am interested in being a Research Intern for Summer 2020.

I believe I have the qualifications in programming, machine learning, and cloud service management to develop and deploy valuable and performant models.
Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
I am looking to work on larger and more complex models that operate with a great deal of data.

I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
I have built reinforcement learning environements using OpenAI's Gym package and am excited to implement larger models in production.
My ideal conversation with an employee would be about how AI is changing the industry and what creative uses of AI in commerce there are.

>>>>

\begin{letter}{Impossible Foods \\ Redwood City, CA}

\opening{\textbf{Dear Impossible Foods,}}

I am interested in being a Data Science Intern for Summer 2020.

I believe I have the qualifications in programming, machine learning, and cloud service management to provide valuable insights on social media sentiment.
Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
I am looking to work on larger and more complex models, such as BERT and GPT-2.

I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
My ideal conversation with an employee would be about how simulation and machine learning can be used to continually improve the Impossible Burger.

### 2020-03-16 random/career_preparation/cover_letters/pg_and_e.tex
simple website in js/

\begin{letter}{Impossible Foods \\ Redwood City, CA}

\opening{\textbf{Dear Impossible Foods,}}

I am interested in being a Data Science Intern for Summer 2020.

I believe I have the qualifications in programming, machine learning, and cloud service management to provide valuable insights on social media sentiment.
Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
I am looking to work on larger and more complex models, such as BERT and GPT-2.

I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
My ideal conversation with an employee would be about how simulation and machine learning can be used to continually improve the Impossible Burger.

>>>>

\begin{letter}{Pacific Gas and Electric \\ 77 Beale Street \\ San Francisco, CA 94105}

\opening{\textbf{Dear Pacific Gas and Electric,}}

I am interested in being an Meteorology Data Science Intern for Summer 2020.

I believe I have the qualifications in programming, machine learning, and deploying cloud services to make a helpful contribution towards creating innovative predictive models.
Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
I am looking to implement larger scale models that use interesting data and require innovative models, which meteorology requires.

My ideal conversation with an employee would be about what architectures and models are used currently in meteorology and what the constraints are of these models.

### 2020-03-16 random/career_preparation/cover_letters/pocket_gems.tex
simple website in js/

\begin{letter}{JD \\ JD Building, No. 18 \\ Kechuang 11 Street \\ BDA, Beijing, 101111}

\opening{\textbf{Dear JD,}}

I am interested in being a Research Intern for Summer 2020.

I believe I have the qualifications in programming, machine learning, and cloud service management to develop and deploy valuable and performant models.
Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
I am looking to work on larger and more complex models that operate with a great deal of data.

I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
I have built reinforcement learning environements using OpenAI's Gym package and am excited to implement larger models in production.
My ideal conversation with an employee would be about how AI is changing the industry and what creative uses of AI in commerce there are.

>>>>

\begin{letter}{Pocket Gems \\ 220 Montgomery Street \\ San Francisco, CA 94104}

\opening{\textbf{Dear Pocket Gems,}}

I am interested in being a Data Science Intern for Summer 2020.

I believe I have the qualifications in programming, machine learning, and cloud service management to develop and deploy valuable and performant models.
Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
I am looking to work on larger and more complex models.

I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
I have built reinforcement learning environements using OpenAI's Gym package and am excited to implement larger models in production.
My ideal conversation with an employee would be about how AI is changing the gaming industry and what creative uses of AI in gaming there are.

### 2020-03-16 random/career_preparation/cover_letters/qurip.tex
simple website in js/

\address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
% \address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number

@@

\begin{letter}{Intel Corporation \\ 2200 Mission College Blvd \\ Santa Clara, CA  95052 }

\opening{\textbf{Dear Intel,}}

>>>>

% \address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
\address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number

@@

\begin{letter}{QURIP Internship}

\opening{\textbf{Dear QURIP,}}

Almost every quantum scientist knows Feynmans’ holy quote, "Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical".

### 2020-03-16 random/career_preparation/cover_letters/wing.tex
simple website in js/

\begin{letter}{Skydio \\ 114 Hazel Ave \\ Redwood City, CA 94061}

\opening{\textbf{Dear Skydio,}}

I am interested in being an Autonomy Intern for Summer 2020.

I believe I have the qualifications in machine learning, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of drone technology. Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. I am looking to further my understanding of the stack by working on embedded machine learning.

I have taken an electronics course, where we built radios, stopwatches, and other things in VDHL, as well as an interactive devices course that taught 3D printing and wearable device building. My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice. The current solution is tractors and manually dispersing the salt. I would like to see drones be able to quickly provide a map of unwalkable locations and report this to people cleaning up snow.

>>>>

\begin{letter}{Wing  \\ Palo Alto, CA 94304}

\opening{\textbf{Dear Wing,}}

I am interested in being an Engineering Intern for Summer 2020.

I believe I have the qualifications in programming, machine learning, and electronics to make a helpful contribution towards creating innovative applications of Wing planes.
Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
I am looking to further my understanding of the stack by working on embedded machine learning.

I have taken an electronics course, where we built radios, stopwatches, and other things in VDHL, as well as an interactive devices course that taught 3D printing and wearable device building. 
My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: 
At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice. 
The current solution is tractors and manually dispersing the salt. 
I would like to see planes map unwalkable locations and report this to people cleaning up snow.
